%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Five9} % Organisation
    {Remote, Portugal} % Location
    {Oct 2023 - Jun 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Seeded and promoted the growth of a new data team that took over the on-going reporting modernization efforts.}
        \item {Identified and solved correctness issues on the architecture of type II dimension pipelines.}
        \item {Identified and solved scaling bottlenecks on event processing service reducing peak usage from 1200 pods to 80 pods with a load of 70 MiB/sec.}
        \item {Improved existing data pipeline reducing data loss by 98\% and increasing data quality.}
        \item {Endorsed improvements on event processing resiliency, identified significant cost deficiencies, promoted development of tooling to ease investigation work, as well as changes to simplify the existing architecture. }
        \item {Contributed to the architecture and development of an event processor to support customer billing use-cases within the company.}
        \item {Onboarded and supported other business areas into contributing to our wide-table and dimension datasets to satisfy their reporting needs.}
        \item {\textbf{Technical skills:} Java, GCP Pub/Sub, GCP BigQuery, GCP Datastore, GCP Storage, Looker.}
      \end{cvitems}
    }
    
  \cventry
    {Software Engineer II} % Job title
    {Talkdesk} % Organisation
    {Remote, Portugal} % Location
    {Nov 2020 - Jul 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintained an event-sourcing data platform based on kafka-streams that processed 20M events / hour into a Lakehouse with TiB of data.}
        \item {Developed a new generation of the platform based on Flink to promote autonomous development of event-sourcing and CDC data pipelines by other teams.}
        \item {Improved query performance by 80\% on a streaming API with end-to-end SLO of 5s by redesigning the data model.}
        \item {Migrated critical data pipelines to Flink reducing end-to-end latency, deployment time, and mitigating resiliency issues.}
        \item {Designed a scheduler for an asynchronous API that generated data reports, eliminating bugs and reducing customer complaints.}
        \item {Worked with an engineering team to increase communication, motivate technical discussion and investigation work.}
        \item {\textbf{Technical skills:} Kafka, Kafka Streams, Flink, RabbitMQ, Iceberg, Looker, Trino, Vitess, ScyllaDB, Scala, Kotlin, Elixir.}
      \end{cvitems}
    }

  \cventry
    {Software Engineer} % Job title
    {Feedzai} % Organisation
    {Porto, Portugal} % Location
    {Sep 2019 - Aug 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked as a Backend Engineer on the real-time fraud detection engine.}
        \item {Transitioned to Customer Success Engineer and dealt directly with clients, customizing their unique solutions and preparing their Go-Live.}
        \item {\textbf{Technical skills:} Java, Ansible.}
      \end{cvitems}
    }


  \cventry
    {Intern} % Job title
    {United Technologies Research Centre} % Organisation
    {Cork, Ireland} % Location
    {Feb 2019 - Jul 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on a proof-of-concept that generated Simulink monitors based on natural language requirements to assist engineers during the design of embedded systems. This project was the dissertation for my master's degree.}
        \item {\textbf{Technical skills:} Python, Linear Temporal Logic, Simulink.}
      \end{cvitems}
    }

\end{cventries}
